No Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts

### 2024-01-22 outputs/paper/paper.qmd
created 3 graphs representing correlations

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: false
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

```{r}
#| label: fig-coded
#| fig-cap: Visualization to show correlation between number of Calls Coded and Homeless Death Counts
#| echo: false

homeless_death_counts <- read_csv(here::here("outputs/data/cleaned_homeless_death_counts.csv"), show_col_types = FALSE)
central_intake_call <- read_csv(here::here("outputs/data/cleaned_central_intake_call.csv"), show_col_types = FALSE)

ggplot(homeless_death_counts, aes(x = Date_month, y = Count)) + 
  geom_bar(stat = "identity", fill = "lightsteelblue", color = "lightsteelblue") +
  geom_line(data = central_intake_call, aes(x = Month, 
    y = Calls_Coded_month/1000)) +
  labs(
    title = "Correlation between number of Calls Coded and Homeless Death Counts",
    x = "Date",
    Y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

```{r}
#| label: fig-referred
#| fig-cap: Visualization to show correlation between number of callers referred to shelter and Homeless Death Counts
#| echo: false

homeless_death_counts <- read_csv(here::here("outputs/data/cleaned_homeless_death_counts.csv"), show_col_types = FALSE)
central_intake_call <- read_csv(here::here("outputs/data/cleaned_central_intake_call.csv"), show_col_types = FALSE)

ggplot(homeless_death_counts, aes(x = Date_month, y = Count)) + 
  geom_bar(stat = "identity", fill = "lightsteelblue", color = "lightsteelblue") +
  geom_line(data = central_intake_call, aes(x = Month, 
    y = Referral_to_Shelter_month/100)) +
  labs(
    title = "Correlation between # of Callers Referred to Shelter and Homeless Death Counts",
    x = "Date",
    Y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

```{r}
#| label: fig-informed
#| fig-cap: Visualization to show correlation between number of callers given information on homelessness prevention and Homeless Death Counts
#| echo: false

homeless_death_counts <- read_csv(here::here("outputs/data/cleaned_homeless_death_counts.csv"), show_col_types = FALSE)
central_intake_call <- read_csv(here::here("outputs/data/cleaned_central_intake_call.csv"), show_col_types = FALSE)

ggplot(homeless_death_counts, aes(x = Date_month, y = Count)) + 
  geom_bar(stat = "identity", fill = "lightsteelblue", color = "lightsteelblue") +
  geom_line(data = central_intake_call, aes(x = Month, 
    y = Information_Homelessness_and_Prevention_month/100)) +
  labs(
    title = "Correlation between number of Callers given Information on Homelessness Prevention and Homeless Death Counts",
    x = "Date",
    Y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```
